### 2020-10-27 treatise/4_simulation.tex
Update figures

In the following, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively.
Plots 1 to 5 have \m {N_H = 3 N_Y}, and the plots 6 to 10 has \m {N_H = 2 N_Y}.
%
\blank [big]
%\externalfigure [assorted-wide-very-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [assorted-wide-very-big-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [assorted-narrow-very-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [assorted-narrow-very-big-error.png] [wfactor=fit, hfactor=fit]

As of the plot of time taken in minutes, we give only one of \m {N_H = 18}, as an example.
%
\blank [big]
\externalfigure [assorted-medium-time.png] [wfactor=fit, hfactor=fit]

@@

%
\blank [big]
%\externalfigure [ddss-very-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [ddss-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [ddss-medium-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [ddss-big-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [ddss-very-big-error.png] [wfactor=fit, hfactor=fit]
%
As of the plot of time taken in minutes, we give only one of \m {N_H = 16}, as an example.
%
\blank [big]
\externalfigure [assorted-medium-time.png] [wfactor=fit, hfactor=fit]

@@

%
\blank [big]
%\externalfigure [oommpp-very-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [oommpp-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [oommpp-medium-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [oommpp-big-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [oommpp-very-big-error.png] [wfactor=fit, hfactor=fit]
%
As of the plot of time taken in minutes, we give only one of \m {N_H = 16}, as an example.
%
\blank [big]
\externalfigure [assorted-medium-time.png] [wfactor=fit, hfactor=fit]

>>>>

In the following, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively.
Plots 1 to 5 have \m {N_H = 3 N_Y}, and the plots 6 to 10 has \m {N_H = 2 N_Y}.
%
\blank [big]
%\externalfigure [assorted-wide-very-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [assorted-wide-very-big-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [assorted-narrow-very-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [assorted-narrow-very-big-error.png] [wfactor=fit, hfactor=fit]

As of the plot of time taken in minutes, we give only one of \m {N_H = 12}, as an example.
%
\blank [big]
\externalfigure [assorted-small-time.png] [wfactor=fit, hfactor=fit]

@@

%
\blank [big]
%\externalfigure [ddss-very-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [ddss-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [ddss-medium-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [ddss-big-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [ddss-very-big-error.png] [wfactor=fit, hfactor=fit]

@@

%
\blank [big]
%\externalfigure [oommpp-very-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [oommpp-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [oommpp-medium-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [oommpp-big-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [oommpp-very-big-error.png] [wfactor=fit, hfactor=fit]
